Best Practices for Single Alchemical Free Energy Calculations [Article v\versionnumber]

### 2025-02-11 paper/manuscript.tex

%%%%%%%%%%%%%%%%%%%%
% Theory basics    %
%%%%%%%%%%%%%%%%%%%%
\section{\tocorange{Statistical mechanics demonstrates why alchemical free energy calculations work}}
%\section{\tocorange{Statistical mechanics theory of solvation, solvent partitioning, and binding}}
\tocsectioncomment{Steering Meeting: @Emilio Gallicchio to update theory. @Stefan Boresch to comment on dummy atom considerations? Will frame it to be as general as possible, while remaining accessible to beginners. Will align with Gilson et al. 1997 paper. @Darrin York to review.}
\label{sec:theory}

@@

Combining Eqs.~(\ref{eq:DG-solvation-excess}) and (\ref{eq:zratio-solv-average}) yields
\begin{equation}
  \Delta G_{\mathrm{slv, exc.}} = - k_B T \ln \langle e^{-\beta \Delta U} \rangle_0 = k_B T \ln \langle e^{\beta \Delta U} \rangle_1
  \label{eq:zratio-solv-dgexc}
\end{equation}
The objective of alchemical solvation free energy calculations is to evaluate Eq.~(\ref{eq:zratio-solv-dgexc}), by means of \emph{coupling} or \emph{decoupling} protocols.

>>>>

%%%%%%%%%%%%%%%%%%%%
% Theory basics    %
%%%%%%%%%%%%%%%%%%%%
\section{\tocgreen{Statistical mechanics demonstrates why alchemical free energy calculations work}}
%\section{\tocorange{Statistical mechanics theory of solvation, solvent partitioning, and binding}}
\label{sec:theory}

@@

Combining Eqs.~(\ref{eq:DG-solvation-excess}) and (\ref{eq:zratio-solv-average}) yields\cite{widom1982potential} 
\begin{equation}
  \Delta G_{\mathrm{slv, exc.}} = - k_B T \ln \langle e^{-\beta \Delta U} \rangle_0 = k_B T \ln \langle e^{\beta \Delta U} \rangle_1
  \label{eq:zratio-solv-dgexc}
\end{equation}
The objective of alchemical solvation free energy calculations is to evaluate Eq.~(\ref{eq:zratio-solv-dgexc}), by means of \emph{coupling} or \emph{decoupling} protocols.
